Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-31 VMCAI-revised-version/final.tex
Re-basculé sur Minsky resilience pour l'indec des reset-VASS

We now prove that {\sc Resilience} is undecidable for reset-VASS when $\Safe = \mathop{\downarrow} \Safe$. We will use the undecidability of the structural existential halting problem.
%
%			hence it will be also undecidable for (upward) compatible WSTS when $\Safe = \mathop{\downarrow} \Safe$.
%
%Indeed, the structural existential halting problem consists in deciding if 
%a system %terminates
%have a terminating (i.e. finite) run
% from every initial state.

>>>>

We now prove that {\sc Resilience} is undecidable for reset-VASS when $\Safe = \mathop{\downarrow} \Safe$.

\mathieu{J'ai remis une vielle version que j'avais écrit avant de basculer sur le structural existential halting, je pense guarder ça en main text et détailler davantage dans l'appendix dit moi ce que tu en pense}
In the case of $\pred$-basis-effective upward compatible WSTS, {\sc Resilience} is undecidable when $\Safe = \mathop{\downarrow} \Safe$.

\begin{proposition}\label{indec WSTS with dcs}
{\sc Resilience} is undecidable for reset-VASS, hence it is also undecidable for $\pred$-basis-effective $\omega^2$-WSTS with strong compatibility and with 
$\Safe=\mathop{\downarrow} \Safe$.
\end{proposition}

\begin{proof}
First, note that {\sc Resilience} is undecidable for a Minsky machine $M$ with at least $2$ counters when
$\Safe = \mathop{\downarrow} \Safe$,
since it is possible to have $\Safe = \{q_f(0,0)\}$. 
Now, executions of Minsky machines can be simulated by reset-VASS~\cite{araki1976PN,dufourd1998reset} in such a way that any sequence 
% from  a state $p({\bf u})$
% to
reaching
 a state 
%
$ q({\bf 0})$ corresponds to one that reaches 
$q_f(0,0)$
 in the Minsky machine and vice versa.
  By combining both constructions, which can be seen in more details in Appendix~\ref{minsk},
 we obtain that 
 {\sc Resilience} is undecidable for reset-VASS when $\Safe = \downarrow \Safe$, and hence for  $\post$-effective, $\pred$-basis-effective, 
$\omega^2$-WSTS with strong compatibility as well.\qed \end{proof}

We will use the undecidability of the structural existential halting problem.
%
%			hence it will be also undecidable for (upward) compatible WSTS when $\Safe = \mathop{\downarrow} \Safe$.
%
%Indeed, the structural existential halting problem consists in deciding if 
%a system %terminates
%have a terminating (i.e. finite) run
% from every initial state.
